---
title: "STAT-612 Final Project"
author: "Haiman Wong"
date: "4/17/2021"
output: word_document
---

```{r}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(tidytext)
library(tm)
library(wordcloud2)
library(ggwordcloud)
```

Processing and Accessing the Dataset
```{r}
setwd("/Users/haimanwong/Desktop")
read_csv("cyberincidents2.csv") -> cyberincidentsdata
cyberincidentsdata

View(cyberincidentsdata)
```

DATA VISUALIZATION
Model 1:Frequency of State B
```{r}
cd<- ggplot(cyberincidentsdata, aes(x="", y = Name, fill=StateB))+
  geom_bar(width = .5, stat = "identity") 
cd

pie <- cd + coord_polar("y", start=0) 
pie
```

Model 2: Bar Graph of Interaction Types Against Method Type** 
```{r}
ggplot(data = cyberincidentsdata) +
  geom_bar(mapping = aes(x = interactiontypename, y = methodname, fill = interactiontypename), stat = "identity")
```

slide 5 wordcloud
```{r}
#unnest words
cyber_words <- cyber %>%          
  unnest_tokens(word,`Political Objective`)
#separated words from political objective column

cyberstop <- cyber_words %>%
  anti_join(stop_words)
#removed stopwords

wordc<-cyberstop %>%
  count(word)%>%
  filter(n>5)

wordcloud2(data=wordc,size = 1.5,color = 'random-light',backgroundColor = 'Black')
```


Model 3: Bar Graph of Interaction Types** (slide 7)
```{r}
ggplot(data = cyberincidentsdata) +
  geom_bar(mapping = aes(x = interactiontypename, fill = interactiontypename))
```

Model 4: Bar Graph of Method Types** (slide 9)
```{r}
ggplot(data = cyberincidentsdata) +
  geom_bar(mapping = aes(x = methodname, fill = methodname))
```

Model 5: Bar Graph of Target Type** (slide 8)
```{r}
ggplot(data = cyberincidentsdata) +
  geom_bar(mapping = aes(x = targettypename, fill = targettypename)) 
```

Model 6: Bar Graph of Cyber Objectives** (slide 8)
```{r}
ggplot(data = cyberincidentsdata) +
  geom_bar(mapping = aes(x = cyber_objectivename, fill = cyber_objectivename))
```

Model 7: Bar Graph of Damage Type** (slide 9)
```{r}
ggplot(data = cyberincidentsdata) +
  geom_bar(mapping = aes(x = damagetypename, fill = damagetypename))
```

slide 10
```{r}
#damagetypename and severity 
#there is only one indirect and delayed
ggplot(cyber,(aes(damagetypename,severity)))+
  geom_boxplot(aes(fill=damagetypename))+
  scale_fill_brewer(palette="Dark2")+
  labs(x='damage type',y='severity',title='Damage Type and Severity')+
  coord_flip()
```

slide 11
```{r}
cyber%>%
  select(targettypename,severity)%>%
  group_by(targettypename)%>%
ggplot(aes(targettypename,severity))+
  geom_violin(aes(group=targettypename,fill=targettypename),show.legend = F)+
   theme_classic()+
  labs(x='type of target',title='Severity and Target Type')

cyber%>%
  select(targettypename,severity)%>%
  group_by(targettypename)%>%
  ggplot(aes(targettypename,severity))+
  geom_boxplot(aes(group=targettypename,fill=targettypename),show.legend = F)+
  theme_classic()+
  labs(x='type of target',title='Severity and Target Type')
```

slide 12
```{r}
cyber %>%
  select(victimname,severity)%>%
  group_by(severity)%>%
  count(victimname)%>%
  arrange(desc(severity))%>%
  ggplot(aes(victimname,n))+
  geom_point(aes(color=factor(severity)))+
  facet_wrap(~severity)+
  coord_flip()+
  labs(x='victim name',y='count',title='Severity of Cyber Attacks')
```

slide 13
```{r}
cyber %>%
  group_by(methodname)%>%
  count(initiatorname)%>%
  arrange(desc(n))%>%
  filter(n>1)%>%
  ggplot(aes(initiatorname,n))+
  geom_col(aes(fill=methodname))+
  scale_fill_brewer(palette="Dark2")+
  coord_flip()+
  labs(x='count',y='country',title='What attack methods do initiators prefer?')
```


Model 8: Scatter Plot of Interaction Start Date vs Cyber Incident Num** (slide 14)
```{r}
ggplot(data=cyberincidentsdata) +
  geom_point(mapping = aes(x = interactionstartdate, y= Cyberincidentnum)) 
```

Model 9: Scatter Plot of Interaction End Date vs Cyber Incident Num** (slide 14)
```{r}
ggplot(data=cyberincidentsdata) +
  geom_point(mapping = aes(x = interactionenddate, y= Cyberincidentnum)) 
```

slide 15
```{r}
cyberregion<-cyber %>%
  group_by(victimregion)%>%
  count()
cyberregion
cd<- ggplot(cyberregion, aes(x="", y = n, fill=victimregion))+
  geom_bar(width = .5, stat = "identity") 
cd

pie <- cd + coord_polar("y", start=0) 
pie+scale_fill_brewer(palette="Dark2")+
  labs(title='Which Region Had the Most Victims?')
```


Model 9: Bar Graph Attempt of Initiator Name and Victim Name
```{r}
ggplot(data = cyberincidentsdata) +
  geom_bar(mapping = aes(x = initiatorname, y = victimname, fill = Name), stat = "identity")
```

Simple Linear Regression (slide 16)
```{r}
lm(Cyberincidentnum~StateA, data = cyberincidentsdata) -> lm1
lm1
```

```{r}
summary(lm1)
```

slide 17
```{r}
lm(damagetype~severity, data = cyberincidentsdata) -> lm2
lm2
```


```{r}
summary(lm2)
```

slide 18
```{r}
lm(initiator~cyber_objective, data = cyberincidentsdata) -> lm3
lm3
```

```{r}
summary(lm3)
```


Multiple Linear Regression (slide 19)
```{r}
lm(Cyberincidentnum~initiator+cyber_objective+damagetype+severity, data = cyberincidentsdata) -> mlr1
mlr1
```

```{r}
summary(mlr1)
```


```{r}
lm(Cyberincidentnum~+methodname+damagetype+severity, data = cyberincidentsdata) -> mlr2
mlr2
```

```{r}
summary(mlr2)
```

slide 20
```{r}
lm(initiator~+targettypename+damagetype+severity, data = cyberincidentsdata) -> mlr3
mlr3
```

```{r}
summary(mlr3)
```

slide 21
```{r}
mlr3<-lm(severity~initiator++method+interactiontype, data = cyberincidentsdata)
mlr3
```

```{r}
summary(mlr3)
```


T-Test
```{r}
t.test(interactionstartdate~initiatorname, data = cyberincidentsdata)
```

Suppose APT is Y variable (slide 22) 
```{r}
glm(formula = APT ~ interactiontype + severity + targettype + cyber_objective + information_operation + objective_achievement + Concession + X3rdpartyinitator + X3rdparty.target + govtstatement + damage.type, family = binomial(), data = cs)-> cs.ful
summary(cs.ful)
```

slide 23
```{r}
glm(formula = APT ~ interactiontype + severity + information_operation + Concession + X3rdpartyinitator + X3rdparty.target + govtstatement + damage.type, family = binomial(), data = cs)-> cs.reduced
summary(cs.reduced)
```

slide 24
```{r}
anova(cs.ful, cs.reduced, test = "Chisq")
```

slide 25
```{r}
cs1$prob <- predict(cs.reduced,newdata=cs,type="response")
testdata2<-data.frame(interactiontype=mean(cs$interactiontype), severity=seq(0,10,1),information_operation=mean(cs$information_operation),Concession=mean(cs$Concession), X3rdpartyinitator=mean(cs$X3rdpartyinitator), X3rdparty.target=mean(cs$X3rdparty.target), govtstatement=mean(cs$govtstatement), damage.type=mean(cs$damage.type))
testdata2$prob <- predict(cs.reduced,newdata=testdata2,type="response")
testdata2
testdata2%>%
  select(severity, prob)
```

